Towards ....

### 2015-03-24 paper/nodalida2015.tex
more text and add refs

\documentclass[11pt]{article}
\usepackage{nodalida2015}
\usepackage{times}
\usepackage{mathptmx}
%\usepackage{txfonts}
\usepackage{url}
\usepackage{latexsym}
\special{papersize=210mm,297mm} % to avoid having to use "-t a4" with dvips 
%\setlength\titlebox{6.5cm}  % You can expand the title box if you really have to

@@

\section{Introduction}
Constraint Grammar (CG) was first introduced by \cite{KarlssonTODO}. 
It is a tool for disambiguating output by morphological analyser.

@@

Application of logic to POS tagging or shallow parsing isn't new;
\cite{lager1998, lager2000} present constraint rules as 
a disjunctive logic program.

@@

Transformation-Based Learning of Rules for CG tagging (the paper with rules where ordering didn't matter so much)

@@

The first

>>>>

\documentclass[11pt]{article}
\usepackage{nodalida2015}
\usepackage{times}
\usepackage{mathptmx}
%\usepackage{txfonts}
\usepackage{url}
\usepackage{latexsym}
\usepackage{cite}
\special{papersize=210mm,297mm} % to avoid having to use "-t a4" with dvips 
%\setlength\titlebox{6.5cm}  % You can expand the title box if you really have to

@@

\section{Introduction}
Constraint Grammar (CG) was first introduced by \cite{karlsson1995constraint}. 
It is a tool for disambiguating output by morphological analyser.

@@

Application of logic to POS tagging or shallow parsing isn't new;
\cite{lager98, lager_nivre01} present constraint rules as 
a disjunctive logic program.

@@

\cite{lager01transformation} showed rules where ordering didn't matter so much in the end.

@@
